\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Caleb Jares}

\section{Objective}

	% \begin{eventList}
	I hope to obtain a full-time internship for the summer of 2013 where I am able to utilize my programming, problem-solving, and creative skills. I welcome an environment where I am challenged every day and look forward to learning new technologies, making lasting connections, and having fun.
	% \end{eventList}

\section{Work Experience}

	\begin{eventlist}

	\item{August 2012 -- Present}
	     {Locabal -- Lincoln, NE}
	     {Web Developer}

		Led the back-end architecture design for \href{http://locabal.com}{Locabal}. Used many technologies including C\# 5.0, ASP.NET MVC 4, and Entity Framework 5. 
		%Locabal is a student-led startup whose mission is to connect producers of handcrafted items with buyers both locally and globally.

	\item{May 2012 -- August 2012}
	     {Intel -- Hillsboro, OR}
	     {System Engineer}

	     Used PowerShell and various command-line tools to automate installations and updates of server instances. Reverse-engineered third-party installers that didn't offer automated installers. 

	\item{March 2012 -- May 2012}
	     {Green Bein' -- Lincoln, NE}
	     {Game Design and Developer}

	     Used Actionscript 3 to develop games, specifically a 2D platformer with social networking capabilities. Contributed and helped refine ideas and major gameplay features.
	     %Worked on the game Synch, a 2D platformer that allows users to share custom created stages through Facebook and Synch's website.

	\item{November 2011 -- May 2012}
	     {UNL - Avery Hall -- Lincoln, NE}
	     {Student Resource Center Assistant}

	     Assisted and taught students in need of homework help for CSCE 101, 102, 155, 156, 230, 235, and 310. Languages included Java, C++, C, and Matlab. Maintained the two CSCE labs and managed student CSCE accounts.
	     %Helped students with computer science homework and provided technical maintenance for the CSE department.

	\end{eventlist}

\personal
    %[c-jar.es]
    {540 N 16th St\newline Room 1218\newline Lincoln, NE 68508}
    {+1 (970) 590-3046}
    {cjares@cse.unl.edu}

\section{Education}

	\begin{yearlist}

	\item[B.S. in Computer Science and Mathematics]{2011 -- 2015}
	     {University of Nebraska-Lincoln}
	     {Lincoln, NE}

	\item[High School Diploma]{2007 -- 2011}
	     {Windsor High School}
	     {Windsor, CO}

	\end{yearlist}

\section{Interests}

	\begin{eventlist}

	\item{}{}{Game Development and Design}

		I am interested in a career in Game Development, and thus would love an internship at a game company. I would like to work with engine development, game design, or internal tools development.}

	\item{}{}{Front-End Web Development}

		Working at Locabal has given me insight into how a web server functions, but I haven't gotten to work on front-end markup, design, and code. I would like the opportunity to strengthen my HTML, CSS, and Javascript skills by spending an internship working with an experienced and knowledgeable team.


	\end{eventlist}

\section{Software skills}

	\begin{factlist}

	\item{Source Control}
		 {Git, Subversion, TFS}

	\item{Markup}
		 {XAML, XML, HTML, \LaTeX, Markdown, YAML}

	\item{Languages}
		 {C\#, PowerShell, Java, C++}

	\item{Frameworks}
		 {Microsoft XNA, .NET 5.0, Entity Framework 5}

	\item{Methodologies}
		 {MVVM, MVC, Dependency Injection, IoC}

	\end{factlist}

\end{document}
